---
title: 'Chapter 6: Linear Model Selection and Regularization'
pdf_document: default
output:
  html_notebook:
    pandoc_args:
    - --number-sections
    - --number-offset=6
    toc: yes
  html_document:
    toc: yes
  pdf_document:
    toc: yes
---

# Overview

Problem: high dimensionality

## Subset Selection
variations
pros, cons

## Shrinkage Methods

## Dimension Reduction

# Lab

## Best Subset Selection

### Original

```{r, message=FALSE}
library(ISLR)

Hitters <- na.omit(Hitters) # remove na values
sum(is.na(Hitters)) # check that na values are removed

# use leaps to find best subset selection by r2
library(leaps)
regfit.full <- regsubsets(Salary ~., Hitters, nvmax = 10)
summary(regfit.full)
```

```{r}
reg.summary <- summary(regfit.full) #summarize models
reg.summary$rsq #see the r2s
```

Plot the the change in RSS and Rsq as the number of variables increase

```{r, message=FALSE}
par(mfrow=c(1,2))
plot(reg.summary$rss, xlab = "Nvar", ylab = "RSS", type = "l")
plot(reg.summary$adjr2, xlab = "Nvar", ylab = "Adj RSq", type = "l")
best_model <- which.max(reg.summary$adjr2)
points(10, reg.summary$adjr2[best_model], col="red", cex = 2, pch=20)
```

Look at the variables selecgted for the best model under different criteria.

```{r}
par(mfrow=c(1,2))
plot(regfit.full, scale = "r2")
plot(regfit.full, scale = "adjr2")
plot(regfit.full, scale = "Cp")
plot(regfit.full, scale = "bic")
```

Look at the coefficients for the sixth model

```{r}
coef(regfit.full ,6)
```


```{r, message=FALSE}
#forward subsetselection
regfit.fwd <- regsubsets(Salary~., data = Hitters, nvmax = 19, method = "forward")
#summary(regfit.fwd)

#backward subsetselection
regfit.bwd <- regsubsets(Salary~., data = Hitters, nvmax = 19, method = "backward")
#summary(regfit.bwd)
```

### Better

https://gist.github.com/dkahle/7942a7eba8aaa026d0bab6a1e9d88580

https://cran.r-project.org/web/packages/dotwhisker/vignettes/dotwhisker-vignette.html


```{r}
library(dotwhisker)

x <- broom::tidy(regfit.full)

dwplot(regfit.full)

m1 <- lm(mpg ~ wt + cyl + disp + gear, data = mtcars)
dwplot(m1)
```


## Choosing the Best Model

### Original

```{r}
set.seed(1)
train <- sample(c(TRUE, FALSE), nrow(Hitters), rep = TRUE)
test <- (!train)
```

